\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Altamirano}{Andrés}
\title{Resume}                               % optional, remove / comment the line if not wanted
\address{Horacio Lespada 3234, Córdoba, Argentina, postcode 5008}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+54 0351-156868163}                   % optional, remove / comment the line if not wanted
\phone[fixed]{+54 0351-4762067}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{tato.altamirano@gmail.com}                               % optional, remove / comment the line if not wanted                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Work Experience}

\vspace{6pt}

\begin{itemize}

\item{\cventry{March 2018--Now}{Software Engineer}{SimTLiX}{Córdoba}{}{\vspace{3pt}Working as part of RedHat Team in Argentina to help improoving performance on a massive data ingestion system for Argentinean customs.
}}{Involved Technologies: Python, Django, Flask, RabbitMQ, DRF, Docker, React, Redux, Elasticsearch, PosgreSQL, etc.}

\vspace{6pt}

\item{\cventry{April 2017--March 2018}{Software Engineer}{Moni Online}{Córdoba}{}{\vspace{3pt}Involved on improving Moni Online System to reduce operations time in order to support higher data process due to high demand request. Also involved on planifying and creating new products for the internal users and other visitors.}}{Involved Technologies: Python, Django, Redis, Ansible, Behave, DRF, AWS, HTML5, JQuery, etc.}

\vspace{6pt}

\item{\cventry{August 2016--April 2017}{Software Engineer}{Globant}{Córdoba}{}{\vspace{3pt}Working as part of the National Geographic development team, helping to create ways for Data sources in order to spread data through several plattforms.}}{Involved Technologies: Python, Django, Flask, RabbitMQ, DRF, Elasticsearch, PosgreSQL, Celery, etc.}

\vspace{6pt}

\item{\cventry{August 2014--August 2016}{Software Engineer}{MobyDigital}{Córdoba}{}{\vspace{3pt}Involved on development of several projects, some of them for Argentina, and others for Netherlands, having direct communication with the client, defining tasks, coordinating teams, and being part of the development also.}}{Involved Technologies: Python, Django, Redis, DRF, PosgreSQL, SQL Server, C\#, HTML5, JQuery, etc.}

\vspace{6pt}

\item{\cventry{August 2013--August 2014}{Software Engineer}{Ministerio De Seguridad}{Córdoba}{}{\vspace{3pt}Helped in the optimization of Repat Information System that is used in all Córdoba for generation and managment of transit infractions.}}{Involved Technologies: C\#, HTML5, AngularJS, ASP.Net MVC and WebForms, Oracle, JQuery, etc.}

\end{itemize}

\section{Education}

\vspace{5pt}

\begin{itemize}

\item{\cventry{2006--2017}{Information Systems Engineer}{Universidad Tecnológica Nacional}{Córdoba}{}{}}

\item{\cventry{2000--2005}{ORIENTATION: Economy and Administrative Management}{Instituto Secundario El Salvador}{Córdoba}{}{}}

\end{itemize}

\vspace{2pt}

\section{Technical skills}

\vspace{6pt}

\begin{itemize}

\item \textbf{Technical Knowledges:} Python, Java, C\#, SQL ElasticSearch, Redis, Monogo, RabbitMQ, Docker, Linux, Django, BDD, Flask, HTML, Jquery, CSS, ReactJs, Redux, Scrum.

\vspace{6pt}

\end{itemize}

\section{Courses}

\vspace{6pt}

\begin{itemize}

\item Microsoft programming .Net Junior and Senior.

\vspace{6pt}

\item Intro to Machine Learning(Udacity online course).

\vspace{6pt}

\item Modern React with Redux(Udemy online course).

\vspace{6pt}

\item Oracle 9i Database administration.

\vspace{6pt}

\item ProFoCo Tics: HTML5 Web Design.

\vspace{6pt}

\item GENEXUS X EVOLUTION 2.

\vspace{6pt}

\end{itemize}

\section{Languages}

\vspace{6pt}

\begin{itemize}

\item \textbf{Spanish:} Native

\vspace{6pt}

\item \textbf{English:} Fluent

\vspace{6pt}

\item \textbf{Portuguese:} Basic

\vspace{6pt}

\end{itemize}

\section{Interests and extra-curricular activity}

\vspace{6pt}

\begin{itemize}

\item{Soccer, Basquet, Boxing, Bike Riding, Pets,travelling, scuba diving, etc}

\vspace{6pt}

\end{itemize}

\end{document}

